Supporting Information

### 2015-09-04 ms.Rmd
how many genes per cluster for each family?

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
bibliography: bib/papersLib.bib
---

@@

*Oryza sativa* ssp. japonica cv. Nipponbare plants were grown in a growth chamber with 70% relative humidity at 30°C during the day and 26°C at night. After 7 weeks in long day conditions (LD; 14 hours light and 10 hours darkness) plants were transferred to short day conditions (SD; 10 hours light and 14 hours darkness) to induce floral transition. Inflorescence meristems were harvested from 6 to 14 days after the change of photoperiod.

@@

Briefly, adaptor trimming was performed with `cutadapt` [@Martin:2011eu] and reads were mapped against the MSUv7 genome and annotation [@Kawahara:2013gh; @Ouyang:2007il] downloaded from Phytozome 10.3 [@Goodstein:2012ho] using `STAR` [@Dobin:2012fg] in 2-pass mode. The `'quantMode'` argument of `STAR` was used for read counting. rRNA and tRNA contamination was estimated using `htseq-count` [@Anders:2014gf] to count the number of reads that mapped to regions annotated as tRNA or rRNA on the Rap-DB (**ref**) or to regions where reads simulated with `wgsim` (https://github.com/lh3/wgsim) from rRNA sequences in the TIGR Plant Repeats Database [@Ouyang:2004ia] also mapped. Differential expression analysis to calculate Log~2~ fold change (L~2~FC) values and transformed read counts was performed with the `DESeq2` package [@Love:2014do]. To determine a strict cutoff for unexpressed genes, expression values in transcripts per million were calculated for each gene [@Li:2010cl; @Wagner:2012jf]. These values were compared to pseudo-expression values calculated from intergenic regions of the genome, using intervals of a similar size distrubution to those used for calculating the 'genic' expression values. For each library, the cutoff was placed at the 95^th^ percentile of the distribution of intergenic expression values. Transformed counts and L~2~FC values from expressed genes were used for soft clustering with the `Mfuzz` package [@Kumar:2007uw] and geneset enrichment analysis with the `gage` package [@Luo:2009kp] respectively. All plots were produced with the `ggplot2` package [@Wickham:2009tn].

@@

The primary sequences of *Arabidopsis thaliana*, *Solanum lycopersicum* and *Oryza sativa* MADS proteins were downloaded by querying Phytozome 10.3 [@Goodstein:2012ho] for the PANTHER family PTHR11945 ('MADS BOX PROTEIN') via the `biomaRt` interface (**refs: PANTHER/BIOMART**).

>>>>

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
bibliography: bib/papersLib.bibtex
---

@@

*Oryza sativa* ssp. *japonica* cv. Nipponbare plants were grown in a growth chamber with 70% relative humidity at 30°C during the day and 26°C at night. After 7 weeks in long day conditions (LD; 14 hours light and 10 hours darkness) plants were transferred to short day conditions (SD; 10 hours light and 14 hours darkness) to induce floral transition. Inflorescence meristems were harvested from 6 to 14 days after the change of photoperiod.

@@

Briefly, adaptor trimming was performed with `cutadapt` [@Martin:2011eu] and reads were mapped against the MSUv7 genome and annotation [@Kawahara:2013gh; @Ouyang:2007il] downloaded from Phytozome 10.3 [@Goodstein:2012ho] using `STAR` [@Dobin:2012fg] in 2-pass mode. The `'quantMode'` argument of `STAR` was used for read counting. rRNA and tRNA contamination was estimated using `htseq-count` [@Anders:2014gf] to count the number of reads that mapped to regions annotated as tRNA or rRNA on the Rap-DB [@Ohyanagi:2006go] or to regions where reads simulated with `wgsim` (https://github.com/lh3/wgsim) from rRNA sequences in the TIGR Plant Repeats Database [@Ouyang:2004ia] also mapped. Differential expression analysis to calculate Log~2~ fold change (L~2~FC) values and transformed read counts was performed with the `DESeq2` package [@Love:2014do]. To determine a strict cutoff for unexpressed genes, expression values in transcripts per million were calculated for each gene [@Li:2010cl; @Wagner:2012jf]. These values were compared to pseudo-expression values calculated from intergenic regions of the genome, using intervals of a similar size distrubution to those used for calculating the 'genic' expression values. For each library, the cutoff was placed at the 95^th^ percentile of the distribution of intergenic expression values. Transformed counts and L~2~FC values from expressed genes were used for soft clustering with the `Mfuzz` package [@Kumar:2007uw] and geneset enrichment analysis with the `gage` package [@Luo:2009kp] respectively. All plots were produced with the `ggplot2` package [@Wickham:2009tn].

@@

The primary sequences of *Arabidopsis thaliana*, *Solanum lycopersicum* and *Oryza sativa* MADS proteins were downloaded by querying Phytozome 10.3 [@Goodstein:2012ho] for the PANTHER family PTHR11945 ('MADS BOX PROTEIN') via the `biomaRt` interface [@Thomas:2003db, @Durinck:2009ki].

### 2015-09-04 si.Rmd
how many genes per cluster for each family?

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
    dev: "CairoPDF"
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
bibliography: bib/papersLib.bib
---

>>>>

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
    dev: "CairoPDF"
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
bibliography: bib/papersLib.bibtex
---
